%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Backend Engineer} % Job title
    {SWAG} % Organization
    {Taipei, Taiwan} % Location
    {Jun. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained/Developed features on a Flask based live streaming service. }
        \item {Developed features using a combination of event-based approach and asynchronous message queue architecture. }
        \item {Incorporate usages of MongoDB aggregations and update pipelines to achieve atomicity on update queries. }
        \item {Developed client-server realtime communication with extensive usage of websockets. }
        \item {Hands on experience with video content encoding/encrypting pipelines. Also optimized the pipeline for efficiency and latency. }
        \item {Gained basic knowledge of live content delivery through rtmp stream endpoints.}
        \item {Leveraged Github Actions for CI actions such as building and pushing images, creating releases and automated release notes.}
        \item {Properly document coding guidelines and conventions inside the team for easier enforcement during code review and development. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Unnotech} % Organization
    {Taipei, Taiwan} % Location
    {Jun. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained/Developed features of several Django microservices. }
        \item {Designed and implemented low-latency odds synchronization/limiting system by mainly using Celery asynchronous tasks. The whole process can be done in less than 30 seconds despite the complex business logic and the vast amount of values (worst case 72k) that would need to be adjusted in one single operation. }
        \item {Built and deployed a microservice that issues interest to users every minute. Can serve 10k active users with very basic resources. }
        \item {Refactored ancient code that was written when better options were not available (eg: bulk\_update in Django ORM)}
        \item {Learned how to deploy Kubernetes microservices on GKE using Helm. }
        \item {Integrated Silk into code base for easier endpoint performance analysis and optimization. }
        \item {Optimized 50+ slow endpoints by utilizing techniques such as prefetching objects from databases, revamp the algorithm, leverage suitable but faster data types...etc }
        \item {Collaborated with a 15-men team using Git with a modified version of git flow. }
        \item {Mentored new comers and help them get on track on time. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Pi Softwares} % Organization
    {Kaohsiung, Taiwan} % Location
    {Mar. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, implemented and deployed several websites in Python with Django framework from scratch.}
        \item {Built fully automated CI/CD pipeline with self hosted git server and DroneCI for code updating. Reduced deployment time by 70\% and eliminated all human command line errors and repetitive work. }
        \item {Built and deployed a highly scalable distributed web crawling system with Scrapy, Ansible and a bunch of single board computers.}
        \item {Implemented data ETL pipeline with Kafka, BeautifulSoup, SQLAlchemy.}
        \item {Automated boring daily chores (SSL certificate renew, daily database backups) by combining shell scripts and cron jobs. }
        \item {Implemented in-site search mechanism with Elasticsearch and fine-tuned it for Chinese usage by installing and configuring related packages.}
        \item {Used Google PageSpeed Insights tool to measure website performance and optimize websites for better user experience. }
        \item {Optimized static file serving with self-compiled Nginx with PageSpeed module. }
        \item {Implemented connection pooling between PostgreSQL databases and applications.}
        \item {Set up logging for backend applications with Elasticsearch, Kibana, Filebeat (Nginx), Prometheus, Grafana and Sentry.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
