%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Backend/DevOps Manager} % Job title
    {SWAG} % Organization
    {Taipei, Taiwan} % Location
    {Aug. 2023 - Nov. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed day to day feature developments/bug triages/emergencies for the SWAG backend team and DevOps team. }
        \item {Improved team development velocity by hiring and enabling members for both teams. }
        \item {Introduced automation to the deployment process, improve application update velocity from less than 3 times per day to over 10+ per day. }
        \item {Reduced cloud costs by 20\% by application optimizations and leveraging sensible discounts while not hurting the customer experience. }
        \item {Reduced critical incidents from twice per month to less than 1 per quarter by leveraging sensible scale-up strategy without increasing the cost. }
        \item {Implemented monitoring/alerts/on-call infrastructure with focus on SLA/SLO/SLI. }
        \item {Reduce reports on livestream playbacks of low latency live streaming by migrating legacy HTTP based streaming to WebRTC. }
      \end{cvitems}
    }

  \cventry
    {Senior Backend Engineer} % Job title
    {} % Organization
    {} % Location
    {Jan. 2022 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Decreased latency of livestreams from 12 seconds to 2 seconds with in-house LLDASH/LLHLS. }
        \item {Led assigned feature developments from start to finish. }
        \item {Implemented in-house VoD encoding with various DRM systems (Fairplay/Widevine/PlayReady). }
      \end{cvitems}
    }

  \cventry
    {Backend Engineer} % Job title
    {} % Organization
    {} % Location
    {Jun. 2020 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained/Developed features on a Flask based live streaming service. }
        \item {Developed client-server realtime communication with extensive usage of websockets. }
        \item {Hands on experience with video content encoding/encrypting pipelines. Also optimized the pipeline for efficiency and latency. }
        \item {Gained basic knowledge of live content delivery through rtmp stream endpoints.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Unnotech} % Organization
    {Taipei, Taiwan} % Location
    {Jun. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained/Developed features of several Django microservices in a team of 15 engineers. }
        \item {Rebuilt odds synchronization system. Reducing processing time from 10+ minutes to under 30 seconds. System supported 100+ executions daily. }
        \item {Built and deployed a microservice that issues interest to users every minute. Can serve 10k active users with very basic resources. }
        \item {Refactored ancient code that was written when better options were not available (eg: bulk\_update in Django ORM)}
        \item {Learned how to deploy Kubernetes microservices on GKE using Helm. }
        \item {Optimized 50+ slow endpoints with various techniques such as profiling, object prefetching, algorithm rewrites, migrating data types...etc }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Pi Softwares} % Organization
    {Kaohsiung, Taiwan} % Location
    {Mar. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, implemented and deployed several websites in Python with Django.}
        \item {Built fully automated CI/CD pipeline with self hosted git server and DroneCI for code updates. Reduced deployment time by 70\% }
        \item {Built and deployed a highly scalable distributed web crawling system with Scrapy, Ansible and a bunch of single board computers.}
        \item {Implemented data ETL pipeline with Kafka, BeautifulSoup, SQLAlchemy.}
        \item {Automated boring daily chores (SSL certificate renew, daily database backups) by combining shell scripts and cron jobs. }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
